% $Id: introduction.tex 65669 2015-01-09 14:55:20Z tgershon $

\section{Introduction}
\label{sec:Introduction}
The \lhcb experiment is one of four detectors making use of CERNs Large Hadron Collider (LHC). The LHC is a circular collider with a 27km circumference that accelerates protons and heavy ions to record breaking energies.  To date a collision energy of 13TeV has been achieved with protons.  The accelerated protons/ions collide at four interaction points around the collider, each of which is surrounded by a detector.  There are two general purpose detectors at the LHC called \atlas and \cms which have a wide range of physics aims.  The other two detectors, however, are designed for more specific physics goals.  One of these detectors, ALICE, is specialised for studying heavy ion collisions.  \lhcb is specialised for studying particles containing beauty quarks in the forward region.

Also, out of the three experiments focused on studying proton-proton (pp) collisions, \lhcb is the only one not focused on direct searches for new physics.  Rather than searching for new particles directly created in the pp collisions, \lhcb searches for new physics by precisely measuring quantities that would be indirectly affected by the presence of physics beyond the standard model (SM).  These measurements include (but are certainly not limited to): Rare decay rates, elements of the CKM (quark mixing matrix) and CP asymmetries.

This report details two distinct areas of my work to date and relevant background information in sections two and three.  Section four details the simulation validation work that has been carried out.  It is impossible to perform a modern particle physics analysis without simulating the production and detection of relevant particles and processes.  This simulation consists of two stages: an event generation stage where the production of relevant particles is simulated and a detector simulation stage where the interaction of these particles with the \lhcb detector is simulated.  Extensive work is carried out to ensure the event generation stage reproduces the correct kinematic distributions, but this report presents validation tests of the detector simulation stage.

Section five presents the second area of my work, which is studies the decay \Bd \to \Kstar \etaz.   This is required before the search for the rare decay \Lb \to p \Km \etaz can be carried out, as it will be used as a control channel.  In general, decays that are forbidden at tree level in the standard model can only proceed via loop diagrams.  As theoretically a large range of particles can contribute to these loop diagrams, any new physics could contribute and change the rate at which this process happens.  By measuring branching fractions and comparing these to standard model predicitons, a search for new physics can be performed.

%LHC- very basic

%LHCb- Goals
%CKM angle measurements
%rare decays
%CP violation
%lepton universality

%LHCb-Achievements

%LHCb-
